\begin{thebibliography}{9}

\bibitem{prince}
    PRINCE, Michael.
    Does Active Learning Work? A Review of the Research.
    \uline{Journal of Engineering Education.}
    93 (3): 223-231, 2004

\bibitem{tsai}
    TSAI, Flora ... [et al.].
    From Boxes to Bees:
        Active Learning in Freshmen Calculus.
    En: IEEE Global Engineering Education Conference
    (4th, 2013, Berlin, Germany)
    Technische Universität Berlin,
    2013,
    pp. 59-68

\bibitem{pejcinovic}
    PEJCINOVIC, Branimir.
    Application of active learning in microwave circuit
        design courses.
    En: ASEE Annual Conference \& Exposition
    (120th, 2013, Atlanta, USA)
    Portland State University,
    2013

\bibitem{scaleup-web}
    SCALE-UP Site [en linea]
    <\url{http://scaleup.ncsu.edu/}>
    [consulta: 16 diciembre 2015]

\bibitem{deslauriers}
    DESLAURIERS, Louis, SCHELEW, Ellen y WIEMAN, Carl.
    Improved learning in a large-enrollment physics class.
    \uline{Science}.
    332(6031): 862–864,
    2011

\bibitem{yuen}
    TSAI, Flora, YUEN, Chau y CHEUNG Ngai-Man.
    Interactive Learning in Pre-University Mathematics.
    En: IEEE International Conference on Teaching,
        Assessment, and Learning for Engineering
    (1st, 2012, Hong Kong, China)
    Hong Kong Polytechnic University,
    2012

\bibitem{handelsman}
    HANDELSMAN, Jo ... [et al.]
    Scientific Teaching.
    \uline{Science}.
    304(5670): 521-522,
    abril, 2004

\bibitem{mills}
    MILLS, Mark.
    The Mobile Revolution Has Only Just Begun [en linea] \\
    <\url{http://www.forbes.com/sites/markpmills/2015/01/19/the-mobile-revolution-has-only-just-begun/}>
    [consulta: 17 diciembre 2015]

\bibitem{gsmai}
    GSMA Intelligence.
    The Mobile Economy 2015 [en linea] \\
    <\url{http://www.gsmamobileeconomy.com/GSMA_Global_Mobile_Economy_Report_2015.pdf}>
    [consulta: 17 diciembre 2015]

\bibitem{plickers}
    Plickers
    <\url{https://plickers.com/}>
    [consulta: 20 diciembre 2015]

\bibitem{lc}
    Learning Catalytics
    <\url{https://learningcatalytics.com/pages/pricing}>
    [consulta: 20 diciembre 2015]

\bibitem{tanenbaum}
    TANENBAUM, Andrew.
    En su: Modern Operating Systems.
    Prentice-Hall.
    1992

\bibitem{tornado}
    Tornado Web Server
    <\url{http://www.tornadoweb.org}>
    [consulta: 22 diciembre 2015]

\bibitem{motor}
    Motor: Asynchronous Python driver for MongoDB
    <\url{http://motor.readthedocs.org}>
    [consulta: 22 diciembre 2015]

\bibitem{rws}
    ReconnectingWebSocket
    <\url{https://github.com/joewalnes/reconnecting-websocket/blob/master/README.md}>
    [consulta: 23 diciembre 2015]

\bibitem{sass}
    Sass (Syntactically Awesome StyleSheets)
    <\url{http://sass-lang.com/documentation/file.SASS_REFERENCE.html}>
    [consulta: 23 diciembre 2015]

\bibitem{bourbon}
    Bourbon
    <\url{http://bourbon.io/}>
    [consulta: 23 diciembre 2015]

\bibitem{coffeescript}
    CoffeeScript
    <\url{http://coffeescript.org/}>
    [consulta: 23 diciembre 2015]

\bibitem{sphinx}
    Sphinx
    <\url{http://sphinx-doc.org/}>
    [consulta: 23 diciembre 2015]

\bibitem{git}
    Git
    <\url{https://git-scm.com/}>
    [consulta: 27 diciembre 2015]

\bibitem{hamari}
    HAMARI, Juho.
    Does Gamification Work? -- A Literature Review of
    Empirical Studies on Gamification.
    En: Hawaii International Conference on System Sciences
    (47th, 2014, Waikoloa, Hawaii)
    Univ. of TampereTampere,
    2014

\end{thebibliography}
